Difference Scores: Paired Samples T-test

### 2024-03-07 examples/_1a_Examples_DifferenceScores_PairedTtests.qmd
example testing

# Create a list of required packages
packages_required <- c("tidyverse", "easystats", "lme4", "gtsummary", "report", "broom", "gridExtra")

@@

@@

knitr::opts_chunk$set(
    echo = T, message = F, warning = F, error = F,
    comment = NA, cache = T, code_folding = T,
    R.options = list(width = 220, digits = 3),
    fig.align = "center",
    out.width = "75%", fig.asp = .75
)
```

@@

```{r}
# Install and load the googledrive package
if (!requireNamespace("googledrive", quietly = TRUE)) install.packages("googledrive")
library(googledrive)

# Authenticate with Google Drive
drive_auth()

<!-- ::: blue
**This code reads in and shows the data to be used in the current
example** -->

@@

@@

df <- my_data

descriptives_table <- df %>%
    select(eventname, sex, race.4level, hisp, anthroweightcalc) %>%
    mutate(eventname = factor(eventname, labels = c("Baseline", "Year 1", "Year 2", "Year 3", "Year 4"))) %>%
    mutate(sex = factor(sex, labels = c("Female", "Male"))) %>%
    tbl_summary(
        by = eventname,
        missing = "no",
        label = list(
            sex ~ "Sex", race.4level ~ "Race", hisp ~ "Hispanic",
            anthroweightcalc ~ "Weight"
        ),
        statistic = list(all_continuous() ~ "{mean} ({sd}) )", all_categorical() ~ "{p}%"),
    ) %>%
    modify_header(all_stat_cols() ~ "**{level}**<br>N = {n}") %>%
    bold_labels() %>%
    italicize_levels() %>%
    modify_spanning_header(all_stat_cols() ~ "**Assessment Wave**")
theme_gtsummary_compact()

@@

**Descriptive Statistics for the weight Variable**
```{r}
## Summary statistics
# Compute summary statistics for weight by eventname
library(dplyr)
summary <- df %>%
    group_by(eventname) %>%
    get_summary_stats(anthroweightcalc, type = "mean_sd")

@@

>>>>

# Create a list of required packages
packages_required <- c("tidyverse","easystats","lme4","gtsummary","report","broom","gridExtra")

@@

```
:::

@@

knitr::opts_chunk$set(echo = T, message=F, warning=F, error=F, 
                      comment=NA, cache=T, code_folding=T,
                      R.options=list(width=220, digits = 3),
                      fig.align='center', 
                      out.width='75%', fig.asp=.75)
```
:::
:::

@@

::: blue
**This code reads in and shows the data to be used in the current
example**

@@

----

<!-- ```{r}
# Install and load the googledrive package
if (!requireNamespace("googledrive", quietly = TRUE)) install.packages("googledrive")
library(googledrive)

# Authenticate with Google Drive

``` -->

```{r}
# Set the URL for the CSV file
file_url <- "https://drive.google.com/file/d/1_gnaEx0wJ28tT0CD_B6mPFwngdfSb6Dr/view?usp=drive_link"

# Set the destination filename
dest_file <- "my_data.rds"

# Download the file
download.file(file_url, destfile = dest_file, mode = "wb")

# Read the CSV file into R
my_data <- readRDS(dest_file)

# Display the first few rows of the data
head(my_data)
```

@@

descriptives_table <- df %>%
  select(eventname, sex, race.4level, hisp, anthroweightcalc) %>%
  mutate(eventname = factor(eventname, labels = c("Baseline", "Year 1","Year 2","Year 3","Year 4"))) %>%
  mutate(sex = factor(sex, labels = c("Female", "Male"))) %>%
  tbl_summary(
    by = eventname,
    missing = "no",
    label = list(sex ~ "Sex", race.4level ~ "Race", hisp ~ "Hispanic", 
                 anthroweightcalc ~ "Weight"),
    statistic = list(all_continuous() ~ "{mean} ({sd}) )", all_categorical() ~ "{p}%"),
  ) %>%
modify_header(all_stat_cols() ~ "**{level}**<br>N = {n}") %>%
  bold_labels() %>%
  italicize_levels() %>%
  modify_spanning_header(all_stat_cols() ~ "**Assessment Wave**")
theme_gtsummary_compact()

@@

**Descriptive Statistics for the weight Variable**
```{r}
## Summary statistics
# Compute summary statistics for weight by eventname
summary <- df %>%
    group_by(eventname) %>%
    get_summary_stats(anthroweightcalc, type = "mean_sd")

@@

## Wrapping Up

::: panel-tabset
### Write-up {.tabset .tabset-fade .tabset-pills}

::: blue
In the study sample, the average weight at baseline was approximately `r summary$mean[summary$eventname == "baseline_year_1_arm_1"]` units with a standard deviation of `r summary$sd[summary$eventname == "baseline_year_1_arm_1"]`, which showed a noticeable increase to an average of `r summary$mean[summary$eventname == "1_year_follow_up_y_arm_1"]` units by Year_1. A one-sample t-test was conducted to determine if the mean difference in weight from baseline to Year_1 significantly deviated from zero. The results indicated a statistically significant increase with a mean difference of approximately `r round(test_result$estimate, 2)` units (`r round(test_result$conf.int[1], 2)` to `r round(test_result$conf.int[2], 2)`), t(`r test_result$parameter`) = `r round(test_result$statistic, 3)`, p < `r test_result$p.value`. Further, a scatterplot visualizing the relationship between baseline and Year_1 weights showed a strong positive linear trend. This suggests that participants who were taller at baseline generally remained taller at Year_1, reaffirming the consistent growth trend observed in the data.
